A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-09 MSR-Scratch.tex
Size and summary statistics tables

>>>>

\begin{table}[ht]
	\centering
	\begin{tabular}{lr}
		\hline
		Projects & 250,163 \\
		Non-empty projects & 233,491 \\
		Remixes of other projects & 12,167 \\
		Usernames & 109,960 \\
		Scripts & 4,049,356 \\
		Blocks & 36,085,654 \\
		Custom block definitions & 209,769 \\
		Projects analyzed by Dr. Scratch & 231,050 \\
		\hline
	\end{tabular}
	\caption{Dataset contents}
	\label{tbl-size}
\end{table}

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
			Projects per username&2.27&1&1&1&2&868\\
			Sprites per project&5.30&0&1&2&5&525\\
			Scripts per project&16.19&0&2&4&11&3,038\\
			Blocks per project&144.25&0&9&26&69&34,622\\
			Custom block definitions per project&0.64&0&0&0&0&372\\
			Total views per project&5.76&0&1&1&4&27,993\\
			Total remixes per project&197.12&0&0&0&0&14,951,164\\
			Total favorites per project&0.54&0&0&0&0&2,582\\
			total-loves&0.41&0&0&0&0&1940\\
			Dr. Scratch mastery score per project&8.92&0&6&8&11&21\\
		\hline
	\end{tabular}
	\caption{Summary statistics of the dataset}
	\label{tbl-stats}
\end{table*}
